### 2023-04-23 manuscript.tex
Merge pull request #319 from SORTEE-Github-Hackathon/pedrohbraga-patch-1 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/8d5bc4ece59c37b94e74db337e837df52f6ac713.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/8d5bc4ece59c37b94e74db337e837df52f6ac713/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4779316109

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/89a66fa3126d65456724dfec0cc1b21af4fed1e0/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/89a66fa3126d65456724dfec0cc1b21af4fed1e0}{SORTEE-Github-Hackathon/manuscript@89a66fa}
on April 23, 2023.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/8d5bc4ece59c37b94e74db337e837df52f6ac713/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/8d5bc4ece59c37b94e74db337e837df52f6ac713}{SORTEE-Github-Hackathon/manuscript@8d5bc4e}
on April 23, 2023.
